### 2025-05-16 draft.tex
docs: Update draft text

% Created 2025-05-16 Fri 08:47
% Intended LaTeX compiler: pdflatex
\documentclass{article}

@@

To demonstrate this utility, we integrated our cp$\backslash$\_measure-based feature extraction into the widely used spatial analysis library Squidpy [CITE]. Being standalone allowed seamless incorporation into workflows powered by the robust SpatialData [CITE] framework underlying Squidpy. Because spatial datasets often comprise significantly more cells per field-of-view (FOV) than conventional microscopy screenings—up to approximately 100,000 cells-traditional software typically cannot process these large images without cropping, which introduces boundary artifacts. Leveraging the modular design of cp$\backslash$\_measure, we parallelized feature extraction at the single-cell level, streaming batches of cells across computational cores. This approach enables efficient computation even on large-scale datasets, a feat not achievable with standard CellProfiler software.

>>>>

% Created 2025-05-16 Fri 08:56
% Intended LaTeX compiler: pdflatex
\documentclass{article}

@@

To demonstrate this utility, we integrated our cp\_measure-based feature extraction into the widely used spatial analysis library Squidpy [CITE]. Being standalone allowed seamless incorporation into workflows powered by the robust SpatialData [CITE] framework underlying Squidpy. Because spatial datasets often comprise significantly more cells per field-of-view (FOV) than conventional microscopy screenings—up to approximately 100,000 cells-traditional software typically cannot process these large images without cropping, which introduces boundary artifacts. Leveraging the modular design of cp\_measure, we parallelized feature extraction at the single-cell level, streaming batches of cells across computational cores. This approach enables efficient computation even on large-scale datasets, a feat not achievable with standard CellProfiler software.
